%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.7in,top=0.4in,right=0.7in,bottom=0.5in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage{graphicx}

%----------------------------------------------------------------------------------------
%   DOCUMENT START
%----------------------------------------------------------------------------------------

\name{Vivek Nathani}
\usepackage{graphicx}
\address{
+91 9106581560 \\ 
viveknathani2402@gmail.com \\ 
\href{https://GitHub.com/viveknathani/}{\underline{GitHub}} \\ 
\href{https://www.linkedin.com/in/viveknathani/}{\underline{LinkedIn}}
}

\begin{document}
\title{Vivek's Resume}
%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{Symbiosis Institute Of Technology}{2019-2023}{B.Tech in Information Technology}{Pune, India}

\vspace{-.65cm}
\item[]
\end{rSubsection}
\end{rSection}


%----------------------------------------------------------------------------------------
%   Projects
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
\begin{rSubsection}{Software Engineer Intern}{June - July 2022}{Investmint}{}
\item Responsible for building an API based trading feature with brokers like Kite (Zerodha) and Dhan.
\item Built APIs for managing user subscriptions.
\item Used technologies like Node.js, PostgreSQL, Redis, and Render.
\end{rSubsection}
\begin{rSubsection}{Full Stack Developer Intern}{November - December 2021}{Iris Aviation - flyi.in}{}
\item Responsible for digitizing their business by building a web application for their needs.
\item Worked on technologies like React, Firebase, and Digital Ocean.
\end{rSubsection}
\end{rSection}

\begin{rSection}{Projects}

\begin{rSubsection}{scrawl - A block based editor}{\href{https://github.com/taskmasterorg/server}{\underline{GitHub}}}{Using Node.js, TypeScript, PostgreSQL,Redis}{}
\item Responsible for writing the backend.
\item Implemented authentication using JSON Web Tokens and Redis.
\item Implemented 2 more services and exposed all of them through a documented API.
\end{rSubsection}

\begin{rSubsection}{assignexpert - Host and grade programming assignments in colleges}{\href{https://github.com/assignexpert/assignexpert}{\underline{GitHub}}}{Using Node.js, TypeScript, PostgreSQL, Redis}{}
\item Implemented the code execution service with support for C, C++, Java, and Python
\item Used bullmq to run background tasks.
\item Implemented CI/CD workflows to lint, build and test.
\
\end{rSubsection}

\end{rSection}

\begin{rSection}{Open source}
{\emph{Some notable open source contributions}}
\begin{rSubsection}{}{}{}{}
\item Wrote tests at google/go-github (\href{https://GitHub.com/google/go-github/pull/2192}{\underline{Merged PR}}).
\item Implemented a feature at google/go-github (\href{https://GitHub.com/google/go-github/pull/2196}{\underline{Merged PR}}).
\item Implemented Kruskal's algorithm at TheAlgorithms/Go (\href{https://GitHub.com/TheAlgorithms/Go/pull/374}{\underline{Merged PR}}).
\end{rSubsection}
\end{rSection}

\begin{rSection}{Achievements and other activities}
\begin{rSubsection}{}{}{}{}
\item Finished at 3rd Position in college with my team in Google Hash Code 2021 with 1,154,975 points.
\item Blogging about my technical experiences and interests over \href{https://vivekn.dev/blog/}{\underline{here}}.
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%   Skills
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & JavaScript (primarily Node.js), TypeScript, Go \\
Tools & Git, Linux, GitHub Actions, MySQL, PostgreSQL, MongoDB \\
\end{tabular}

\end{rSection}

\end{document}
